HTW E1 Testing

### 2023-08-17 Analysis/e1_test.qmd
Inspect Bayesian marginal effects in E1 Test

---
title: "E1 Testing"
categories: [Analysis, R, Bayesian]
---

@@

See @tbl-e1-test-nf-deviation for descriptive statistics of the raw empirical data. 
To assess differences in accuracy between groups, we used Bayesian mixed effects regression models implemented via brms in R. The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (vb), and their interaction, with random intercepts and slopes for each participant (id).

@@

@@

conditional_effects(e1_vxBMM,effects = "bandInt:condit")

>>>>

---
title: "HTW E1 Testing"
categories: [Analysis, R, Bayesian]
---

@@

See @tbl-e1-test-nf-deviation for descriptive statistics of the raw empirical data, and @fig-e1-test-vx for a visual representation of the full distributions.  
To assess differences in accuracy between groups, we used Bayesian mixed effects regression models implemented via brms in R. The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (vb), and their interaction, with random intercepts and slopes for each participant (id).

```{r}
#| label: fig-e1-test-vx
#| fig-cap: E1 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 11
#| fig-height: 9
test %>% group_by(id,vb,condit) |> plot_distByCondit()

@@

```{r}
#| label: fig-e1-bmm-dist
#| fig-cap: E1. Conditioinal Effect of Training Condition and Band. Ribbon indicated 95% Credible Intervals.

e1_distBMM |> emmeans( ~condit +bandInt, 
                       at=list(bandInt=c(100,350,600,800,1000,1200) )) |>
  gather_emmeans_draws() |>
  ggplot(aes(x=bandInt,y=.value,color=condit)) + 
  stat_lineribbon(aes(color=condit,fill=condit),alpha=.45,size=1,.width=c(.95)) + 
  ylab("Predicted Deviation") + xlab("Velocity Band")

@@

#conditional_effects(e1_vxBMM,effects = "bandInt:condit")

e1_vxBMM |> emmeans( ~condit +bandInt, 
                       at=list(bandInt=c(100,350,600,800,1000,1200) )) |>
  gather_emmeans_draws() |>
  ggplot(aes(x=bandInt,y=.value,color=condit)) + 
  stat_lineribbon(aes(color=condit,fill=condit),alpha=.45,size=1,.width=c(.95)) + 
  ylab("Predicted Vx") + xlab("Velocity Band")
